Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-01-18 awipev-CO2.Rmd

at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT_filtered,at)
at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
   #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
  #dySeries("AT_filtered2", color = RColorBrewer::brewer.pal(4, "Set2"), strokeWidth = 0, pointSize=2) %>%
  dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
  dyAxis("y",valueRange = c(2000, 2650)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions( strokeWidth= 0) %>%
  dyLegend(show = "follow")   %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

@@

```{r First period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
# #Interpolation of continuous sensor data to match a maximum of reference data.
# TAinterp_all <-approx(d_all$datetime, d_all$AT_filtered, xout=d_all$datetime, method="linear", rule=2)
# names(TAinterp_all) <- c("datetime", "AT_filtered_interp")
# TAinterp_all <- as.data.frame(TAinterp_all)
# d_all$AT_filtered_interp <- TAinterp_all$AT_filtered_interp
# 
# # create a column with difference between sensor and ref
# d_all <- d_all%>%
#   dplyr::mutate(diff_ta =  at-AT_filtered_interp )
# # create colum with instrument number
# d_all <- d_all %>% 
#   dplyr::mutate(TA_period= ifelse(datetime >= "2016-02-26 00:00:00" & datetime < "2017-02-09 12:00:00", "TA1",
#                             ifelse(datetime >= "2017-02-09 12:00:00" & datetime < "2017-03-10 12:00:00", "TA2",
#                             ifelse(datetime >= "2018-01-07 00:00:00" & datetime < "2018-06-20 00:00:00", "TA3", 
#                             ifelse(datetime >= "2018-07-31 00:00:00" & datetime < "2018-10-30 18:00:00", "TA4", 
#                             ifelse(datetime >= "2018-10-31 09:00:00" & datetime < "2019-01-16 09:00:00", "TA5",
#                             ifelse(datetime >= "2019-01-26 13:25:00" , "TA6", "TA0")))))))
# 
# #remove outliers
# calib_ta_first <- d_all%>%
#   dplyr::select(datetime, closest_datetime,AT_filtered, AT_filtered_interp, at,diff_ta,TA_period)%>%
#   dplyr::filter(TA_period =="TA1" & !is.na(at))
#   #dplyr::filter( !is.na(at))#, diff_ta > -40 & diff_ta < 20 )
# # & datetime != "2016-08-18 08:00:00" & datetime != "2016-12-29 12:00:00 ",!is.na(at))
# 
# # Parameters of regression
# fit <- lm( data=calib_ta_first%>%filter(diff_ta <= 50), diff_ta ~ datetime)
# at_slope_TA1 <- round(fit$coefficients[[2]] , digits=6)
# at_slope1 <- round(at_slope_TA1 * 3600 *24 * 365.24, digits=2)
# at_intercept1 <- round(fit$coefficients[[1]], digits= 2)
```

<!-- The slope is: `r #at_slope_TA1` x 3600 x 24 x 365.24 = `r #at_slope1` µmoles.kg-1.yr-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. Outliers are in red. -->

#```{r First period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
# # Plot of regression
# p <- ggplot(calib_ta_first%>%filter(diff_ta <= 50),aes(datetime,diff_ta)) + 
#     geom_point() + geom_smooth(method='lm', se=FALSE)+ 
#     geom_point(data= calib_ta_first%>%filter(diff_ta >= 50), aes(x=datetime, y=diff_ta), color="red")  +
#   geom_hline(yintercept = 0, linetype="dashed" )+
#   labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
#                      "Intercept =",signif(fit$coef[[1]],5 ),
#                      "Slope =",signif(fit$coef[[2]], 5),
#                      "P =",signif(summary(fit)$coef[2,4], 5))) + 
#   ylab("Difference: Reference - Analyser") + xlab("Time") + scale_x_datetime(date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
# print(p)
# ggsave(paste0("figures/Diff_ref_TA_first_period.png"), p, units="cm")
#```

@@

#```{r Third period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold',fig.align="center"}

# #remove outliers and remove period without TA measurements 
# calib_ta_third <- d_all%>%
#   dplyr::select(datetime, closest_datetime,AT_filtered, AT_filtered_interp, at,diff_ta, TA_period)%>%
#   dplyr::filter(TA_period == "TA3" & !is.na(at))
# 
# # Parameters of regression
# fit <- lm( data=calib_ta_third, diff_ta ~ datetime)
# at_slope_TA3 <- round(fit$coefficients[[2]] , digits=8)
# at_slope3 <- round(at_slope_TA3 * 3600 *24 * 365.24, digits=2)
# at_intercept3 <- round(fit$coefficients[[1]], digits= 2) # pas besoin ici.
#```

<!--The slope is in days: `r #at_slope_TA3` x 3600 x 24 x 365.24 = `r #at_slope3` µmoles.kg-1.an-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. No outliers.
-->

# ```{r Third period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
# # # Plot of regression
#  p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+ 
#      geom_point() + geom_smooth(method='lm', se=FALSE)+ 
#      #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  +
#     geom_hline(yintercept = 0, linetype="dashed" )+
#    geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") +
#    #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+
#    labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
#                       "Intercept =",signif(fit$coef[[1]],5 ),
#                       " Slope =",signif(fit$coef[[2]], 5),
#                       " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") + 
#    scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
#  print(p)
#  ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm")
# ```

@@

# ```{r Second period, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}

# #remove outliers and remove period without TA measurements 
# calib_ta_second <- d_all%>%
#   dplyr::select(datetime, closest_datetime, AT_filtered, AT_filtered_interp, at, diff_ta, TA_period)%>%
#   dplyr::filter(TA_period == "TA2" & !is.na(at))
# 
# mean_offset <- mean(calib_ta_second$diff_ta)

# ```

<!--For the second period, the average difference between 5 discrete samples "references" and TA analyser measurements (`r #mean_offset` µmoles.kg~-1~) was added to TA value as an offset.
-->

@@

<!--The following plot shows the corrected TA data with regressions (Periods 1 and 3) and with offset (Period 2) applied according to Steffen's proposition.
It is clear that these corrected data (in green) cannot be used for periods 1 to 3. The jury is still out for period 4. The issue of salinity must be clarified before an assessment can be made. 
-->

#```{r Correction applied, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}
# # Correction for the 3 periods is apply
# d_all <- d_all%>%
#   dplyr::mutate(datetime_reg = as.numeric(datetime), 
#                 at_intercept = ifelse(TA_period == "TA1", at_intercept1, 
#                                ifelse(TA_period == "TA3", at_intercept3, NA)),
#                 at_slope = ifelse(TA_period == "TA1", at_slope_TA1, 
#                            ifelse(TA_period == "TA3", at_slope_TA3, NA))
#                 )
#                 
# d_all <- d_all%>%
#  dplyr::mutate(TA_reg_corrected = ifelse(TA_period == "TA1", (AT_filtered + (d_all$datetime_reg * d_all$at_slope + at_intercept)),
#                                         ifelse(TA_period == "TA2", (AT_filtered + mean_offset),
#                                         ifelse(TA_period == "TA3", (AT_filtered + (datetime_reg * at_slope)+ at_intercept), NA))))
# 
# at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT_filtered,at,TA_reg_corrected)
# at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
# dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
#    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
#   dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
#   dySeries("TA_reg_corrected", label= "Corrected TA", color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
#   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
#   dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
#   dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
#   dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
#   dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
#   dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
#   dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
#   dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
#   dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
#   dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
#   dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
#   dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
#   dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
#   dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
#   dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
#   dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
#   #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
#   dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
#   dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
#   dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
#   dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
#   dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
#   dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
#   dyAxis("y",valueRange = c(1600, 2650)) %>%
#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
#   dyOptions( strokeWidth= 0) %>%
#   dyLegend(show = "follow")   %>%
#   dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
#     dyRangeSelector(height = 30, dateWindow= NULL)

#```

@@

<!--In the previous part, missing TA were interpolated with a linear model. This does not reflect the natural variability of TA. For this reason, missing TA is now calculated from salinity data by making a relationship between the same reference TA samples as in the previous part and salinity data.
-->

@@

<!--
The relationship between titrated total alkalinity (references) and salinity is very good with an r2 of `r #round(summary(fit)$r.squared, digits=2)`. Need to compare with other relationships from the literature.
-->

>>>>

at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT_filtered,at)
at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
   #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
  #dySeries("AT_filtered2", color = RColorBrewer::brewer.pal(4, "Set2"), strokeWidth = 0, pointSize=2) %>%
  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
  dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
  dyAxis("y",valueRange = c(2000, 2650)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions( strokeWidth= 0) %>%
  dyLegend(show = "follow")   %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

@@

```{r First period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
#Interpolation of continuous sensor data to match a maximum of reference data.
TAinterp_all <-approx(d_all$datetime, d_all$AT_filtered, xout=d_all$datetime, method="linear", rule=2)
names(TAinterp_all) <- c("datetime", "AT_filtered_interp")
TAinterp_all <- as.data.frame(TAinterp_all)
d_all$AT_filtered_interp <- TAinterp_all$AT_filtered_interp

# create a column with difference between sensor and ref
d_all <- d_all%>%
  dplyr::mutate(diff_ta =  at-AT_filtered_interp )
# create colum with instrument number
d_all <- d_all %>%
  dplyr::mutate(TA_period= ifelse(datetime >= "2016-02-26 00:00:00" & datetime < "2017-02-09 12:00:00", "TA1",
                            ifelse(datetime >= "2017-02-09 12:00:00" & datetime < "2017-03-10 12:00:00", "TA2",
                            ifelse(datetime >= "2018-01-07 00:00:00" & datetime < "2018-06-20 00:00:00", "TA3",
                            ifelse(datetime >= "2018-07-31 00:00:00" & datetime < "2018-10-30 18:00:00", "TA4",
                            ifelse(datetime >= "2018-10-31 09:00:00" & datetime < "2019-01-16 09:00:00", "TA5",
                            ifelse(datetime >= "2019-01-26 13:25:00" , "TA6", "TA0")))))))

#remove outliers
calib_ta_first <- d_all%>%
  dplyr::select(datetime, closest_datetime,AT_filtered, AT_filtered_interp, at,diff_ta,TA_period)%>%
  dplyr::filter(TA_period =="TA1" & !is.na(at))
  #dplyr::filter( !is.na(at))#, diff_ta > -40 & diff_ta < 20 )
# & datetime != "2016-08-18 08:00:00" & datetime != "2016-12-29 12:00:00 ",!is.na(at))

# Parameters of regression
fit <- lm( data=calib_ta_first%>%filter(diff_ta <= 50), diff_ta ~ datetime)
at_slope_TA1 <- round(fit$coefficients[[2]] , digits=6)
at_slope1 <- round(at_slope_TA1 * 3600 *24 * 365.24, digits=2)
at_intercept1 <- round(fit$coefficients[[1]], digits= 2)
```

The slope is: `r #at_slope_TA1` x 3600 x 24 x 365.24 = `r #at_slope1` µmoles.kg-1.yr-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. Outliers are in red.

```{r First period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
 # Plot of regression
 p <- ggplot(calib_ta_first%>%filter(diff_ta <= 50),aes(datetime,diff_ta)) +
     geom_point() + geom_smooth(method='lm', se=FALSE)+
     geom_point(data= calib_ta_first%>%filter(diff_ta >= 50), aes(x=datetime, y=diff_ta), color="red")  +
   geom_hline(yintercept = 0, linetype="dashed" )+
   labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                      "Intercept =",signif(fit$coef[[1]],5 ),
                      "Slope =",signif(fit$coef[[2]], 5),
                      "P =",signif(summary(fit)$coef[2,4], 5))) +
   ylab("Difference: Reference - Analyser") + xlab("Time") + scale_x_datetime(date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
 print(p)
 ggsave(paste0("figures/Diff_ref_TA_first_period.png"), p, units="cm")
```

@@

```{r Third period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold',fig.align="center"}

 #remove outliers and remove period without TA measurements
 calib_ta_third <- d_all%>%
   dplyr::select(datetime, closest_datetime,AT_filtered, AT_filtered_interp, at,diff_ta, TA_period)%>%
   dplyr::filter(TA_period == "TA3" & !is.na(at))

 # Parameters of regression
 fit <- lm( data=calib_ta_third, diff_ta ~ datetime)
 at_slope_TA3 <- round(fit$coefficients[[2]] , digits=8)
 at_slope3 <- round(at_slope_TA3 * 3600 *24 * 365.24, digits=2)
 at_intercept3 <- round(fit$coefficients[[1]], digits= 2) # pas besoin ici.
```

The slope is in days: `r #at_slope_TA3` x 3600 x 24 x 365.24 = `r #at_slope3` µmoles.kg-1.an-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. No outliers.

```{r Third period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
# # Plot of regression
 p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+
     geom_point() + geom_smooth(method='lm', se=FALSE)+
     #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  +
    geom_hline(yintercept = 0, linetype="dashed" )+
   geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") +
   #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+
   labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                      "Intercept =",signif(fit$coef[[1]],5 ),
                      " Slope =",signif(fit$coef[[2]], 5),
                      " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") +
   scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
 print(p)
 ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm")
```

@@

```{r Second period, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}

#remove outliers and remove period without TA measurements
calib_ta_second <- d_all%>%
  dplyr::select(datetime, closest_datetime, AT_filtered, AT_filtered_interp, at, diff_ta, TA_period)%>%
  dplyr::filter(TA_period == "TA2" & !is.na(at))

mean_offset <- mean(calib_ta_second$diff_ta)

For the second period, the average difference between 5 discrete samples "references" and TA analyser measurements (`r #mean_offset` µmoles.kg~-1~) was added to TA value as an offset.

@@

The following plot shows the corrected TA data with regressions (Periods 1 and 3) and with offset (Period 2) applied according to Steffen's proposition.
It is clear that these corrected data (in green) cannot be used for periods 1 to 3. The jury is still out for period 4. The issue of salinity must be clarified before an assessment can be made.

```{r Correction applied, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}
# Correction for the 3 periods is apply
d_all <- d_all%>%
  dplyr::mutate(datetime_reg = as.numeric(datetime),
                at_intercept = ifelse(TA_period == "TA1", at_intercept1,
                               ifelse(TA_period == "TA3", at_intercept3, NA)),
                at_slope = ifelse(TA_period == "TA1", at_slope_TA1,
                           ifelse(TA_period == "TA3", at_slope_TA3, NA))
                )

d_all <- d_all%>%
 dplyr::mutate(TA_reg_corrected = ifelse(TA_period == "TA1", (AT_filtered + (d_all$datetime_reg * d_all$at_slope + at_intercept)),
                                        ifelse(TA_period == "TA2", (AT_filtered + mean_offset),
                                        ifelse(TA_period == "TA3", (AT_filtered + (datetime_reg * at_slope)+ at_intercept), NA))))

at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT_filtered,at,TA_reg_corrected)
at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
   #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
  dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
  dySeries("TA_reg_corrected", label= "Corrected TA", color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>%
  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
  dyAxis("y",valueRange = c(1600, 2650)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions( strokeWidth= 0) %>%
  dyLegend(show = "follow")   %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

@@

In the previous part, missing TA were interpolated with a linear model. This does not reflect the natural variability of TA. For this reason, missing TA is now calculated from salinity data by making a relationship between the same reference TA samples as in the previous part and salinity data.

@@

The relationship between titrated total alkalinity (references) and salinity is very good with an r2 of `r #round(summary(fit)$r.squared, digits=2)`. Need to compare with other relationships from the literature.
